---
title: "Alcohol vs Seat choice"
author: "Nicole Orizino"
date: "spring 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  This graph shows the people who drink tend to sit in the back.
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

  This graph shows that the people who sit in the back seats seem to drink significantly more than the people who sit in the middle or front seats.

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

## Inferential Tests
# Inferential

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

  P-value is 0.000116 is a very small number, meaning that is is unlikely that alcohol consumption in all three seat areas is the same. 
  
  
## When significant follow up with TukeyHSD  

```{r}
plot(TukeyHSD(model1))
```

  The tukeyHSD plot shows that the people in the back drink a lot more than the people in the front, people in the middle drink a less than the back and the middle-front shows that there is no evidence in the average alcohol consumption.  

## Conclusions

 The evidence shows that the most people who drink sit in the back seating area.
